---
title: "Text Mining with R"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

Welcome to the "Text Mining with R" FTI session. During this session, we will work through this R Notebook to do some text mining of Jane Austen's works, and turn our results into some charts. Our activities are taken directly from Chapter 1 of "[Text Mining with R: A Tidy Approach](https://www.tidytextmining.com/)" by Silge and Robinson. We're just going to scratch the surface on R and text mining, so if you're interested in pursuing this topic further, take a look at Silge & Robinson's free online text.


Within this R Notebook, we can automatically run code samples by clicking the green triangle button in samples like below (please note that messages beginning with "#" are comments):

```{r}
x<-3  #assigns "3" to variable "x"

x    #prints the value of x

```

Clicking the green triangle is fun and easy, but doesn't really help you learn R. So after each code sample, there will be an empty code block where you can write the code, and then can execute it by clicking the green triangle. In the sample below, create a variable called "y", set it equal to 45, and then print it.

```{r}
#enter your code below:



```


Before really getting going, keep in mind that you can create a web page output of this notebook by clicking the "Preview" button above. It makes this a little easier to read, and also makes this format great for things like tutorials, lab manuals, etc.

### Making our data "Tidy"

One of the big challenges of data science is to take "messy" data, and turn it into "cleaner" data that one can work with. In R, there is a package called the "tidyverse", which establishes some baselines for useful data and R functions to help convert data into "tidy" data. Some key "tidy" data principles are:

* Each variable is a column
* Each observation is a row
* Each type of observational unit is a table

Let's get started by working with a small data set. Below we're going to use the "c" function, to create an array of lines written by Jane Austen, and setting it equal to the variable *text*.

```{r}

text <- c("Because I could not stop for Death -",
          "He kindly stopped for me -",
          "The Carriage held but just Ourselves -",
          "and Immortality")

text

```





Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

